Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-20 rapport.tex
protocol terminé

				\item Share the witness $w$ into an $(N, N)$-threshold linear secret sharing $[w^{[e]}_i]$: \\
				\quad $[X_1^{[e]}], [X_2^{[e]}], [Y_1^{[e]}], [Y_2^{[e]}], [R_A^{[e]}], [R_B^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $\mathbb{F}_{q^k}$. \\
				\quad $[\vec{R}_y^{[e]}], [\vec{R}_y^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $(\mathbb{F}_{q})^n$.

				\item Compute $X_1^{[e]}, X_2^{[e]}, Y_1^{[e]}, Y_2^{[e]}$ \\
				\quad $X_1^{[e]} \leftarrow \sum_{i=1}^{N} [X_1^{[e]}]^{\lir}$. \\
				\quad $X_2^{[e]} \leftarrow \sum_{i=1}^{N} [X_2^{[e]}]^{\lir}$. \\
				\quad $Y_1^{[e]} \leftarrow \sum_{i=1}^{N} [Y_1^{[e]}]^{\lir}$. \\
				\quad $Y_2^{[e]} \leftarrow \sum_{i=1}^{N} [Y_2^{[e]}]^{\lir}$.

				\item Compute $A^{[e]}$ and $B^{[e]}$ and share them: \\
				\quad $A^{[e]} \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B^{[e]} \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A^{[e]} \leftarrow A^{[e]} - \sum_{i=1}^{N} [R_A^{[e]}]^{\lir}$. \\
				\quad $\delta_B^{[e]} \leftarrow B^{[e]} - \sum_{i=1}^{N} [R_B^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_x^{[e]} \leftarrow A^{[e]} - \sum_{i=1}^{N} [\vec{R}_x^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_y^{[e]} \leftarrow A^{[e]} - \sum_{i=1}^{N} [\vec{R}_y^{[e]}]^{\lir}$.

				\item Compute random value $t_0^{[e]}$ and share it. \\
				\quad $[t_0^{[e]}]^{\lir} \leftarrow Hash_0(i || [\vec{R}_x^{[e]}]^{\lir}, [\vec{R}_y^{[e]}]^{\lir}, [X_1^{[e]}]^{\lir}, [X_2^{[e]}]^{\lir}, [Y_1^{[e]}]^{\lir}, [Y_2^{[e]}]^{\lir},$ \\ $[R_A^{[e]}]^{\lir}, [R_B^{[e]}]^{\lir} || \vec{\delta}_x^{[e]}, \vec{\delta}_y^{[e]}, \delta_A^{[e]}, \delta_B^{[e]})$. \\
				\quad $t_0^{[e]} \leftarrow \sum_{i=1}^{N} [t_0^{[e]}]^{\lir}$.

				\item Compute the commitments \\
				\quad $View_i \leftarrow (
				[t_0^{[e]}]^{\lir},
				[(X_1 + t_0(\vec{u} \cdot \vec{x}))^{[e]}]^{\lir},
				[(X_2 + t_0(\vec{v} \cdot \vec{x}))^{[e]}]^{\lir},
				[(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{[e]}]^{\lir},
				[(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{[e]}]^{\lir},
				[(A + t_0 B)^{[e]}]^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(\texttt{salt}, e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 2: First challenge (randomness for the MPC protocol).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute $h_1 := \text{Hash}(m, \texttt{salt}, \texttt{comm}^{[1]}, \dots, \texttt{comm}^{[\tau]})$.
				\item Expand $h_1$ as $(e^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_1)$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Computes, for $i \in S$, \\
				\quad $[\alpha^{[e]}_i] := \varphi_{x,e,f}([w^{[e]}_i], [g^{[e]}_i])$ \\
				and recomposes $\alpha^{[e]}$. \\
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 4: Second challenge (parties to be opened).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute $h_2 := \text{Hash}(\texttt{salt}, h_1, [\alpha^{[1]}]_{S}, \dots, [\alpha^{[\tau]}]_{S})$.
				\item Expand $h_2$ as $(r^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_2)$.
			\end{enumerate}

@@

			\[
			\sigma := \texttt{salt} \parallel h_1 \parallel h_2 \parallel (([w^{[e]}_i], [g^{[e]}_i])_{i \in r^{[e]}}, \texttt{auth}^{[e]}, \alpha^{[e]})_{e \in [1:\tau]}
			\]

			where $\texttt{auth}^{[e]}$ is the authentication path for $\{\texttt{com}^{[e]}_i\}_{i \in r^{[e]}}$ w.r.t. Merkle root $\tilde{h}^{[e]}$ and $i^{[e]} \notin r^{[e]}$.
		\end{tcolorbox}

>>>>

				\item Share the witness $w$ into an $(N-1)$-private linear secret sharing $[w^{[e]}_i]$: \\
				\quad $[X_1^{[e]}], [X_2^{[e]}], [Y_1^{[e]}], [Y_2^{[e]}], [R_A^{[e]}], [R_B^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $\mathbb{F}_{q^k}$. \\
				\quad $[\vec{R}_y^{[e]}], [\vec{R}_y^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $(\mathbb{F}_{q})^n$.

				\item Compute $X_1^{[e]}, X_2^{[e]}, Y_1^{[e]}, Y_2^{[e]}$ \\
				\quad $X_1^{[e]} \leftarrow \sum_{i=1}^{N} [X_1^{[e]}]^{\lir}$. \\
				\quad $X_2^{[e]} \leftarrow \sum_{i=1}^{N} [X_2^{[e]}]^{\lir}$. \\
				\quad $Y_1^{[e]} \leftarrow \sum_{i=1}^{N} [Y_1^{[e]}]^{\lir}$. \\
				\quad $Y_2^{[e]} \leftarrow \sum_{i=1}^{N} [Y_2^{[e]}]^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 2: First challenge (randomness for the MPC protocol).}
			\begin{enumerate}[label=\arabic*.]
				\item Expand $h_1$ as $(e^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_1)$.

				\item Compute random value $t_0^{[e]}$ and share it. \\
				\quad $[t_0^{[e]}]^{\lir} \leftarrow Hash_0(i || [\vec{R}_x^{[e]}]^{\lir}, [\vec{R}_y^{[e]}]^{\lir}, [X_1^{[e]}]^{\lir}, [X_2^{[e]}]^{\lir}, [Y_1^{[e]}]^{\lir}, [Y_2^{[e]}]^{\lir},$ \\ $[R_A^{[e]}]^{\lir}, [R_B^{[e]}]^{\lir} || \vec{\delta}_x^{[e]}, \vec{\delta}_y^{[e]}, \delta_A^{[e]}, \delta_B^{[e]})$. \\
				\quad $t_0^{[e]} \leftarrow \sum_{i=1}^{N} [t_0^{[e]}]^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Compute $A^{[e]}$ and $B^{[e]}$ and share them: \\
				\quad $A^{[e]} \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B^{[e]} \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A^{[e]} \leftarrow A^{[e]} - \sum_{i=1}^{N} [R_A^{[e]}]^{\lir}$. \\
				\quad $\delta_B^{[e]} \leftarrow B^{[e]} - \sum_{i=1}^{N} [R_B^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_x^{[e]} \leftarrow \vec{x}^{[e]} - \sum_{i=1}^{N} [\vec{R}_x^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_y^{[e]} \leftarrow \vec{y}^{[e]} - \sum_{i=1}^{N} [\vec{R}_y^{[e]}]^{\lir}$.

								\item Compute the commitments \\
				\quad $View_i \leftarrow (
				[t_0^{[e]}]^{\lir},
				[(X_1 + t_0(\vec{u} \cdot \vec{x}))^{[e]}]^{\lir},
				[(X_2 + t_0(\vec{v} \cdot \vec{x}))^{[e]}]^{\lir},
				[(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{[e]}]^{\lir},
				[(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{[e]}]^{\lir},
				[(A + t_0 B)^{[e]}]^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$

				\item Compute $h_1 := \text{Hash}(m, \texttt{salt}, \texttt{comm}^{[1]}, \dots, \texttt{comm}^{[\tau]})$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 4: Second challenge (parties to be opened).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute $h_2 := \text{Hash}(\texttt{salt}, h_1, [\alpha^{[1]}]_{S}, \dots, [\alpha^{[\tau]}]_{S})$.
				\item Expand $h_2$ as $(I^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_2)$ where, for every $e, I^{[e]} \in [1:N]$ the party that will not be opened.
			\end{enumerate}

@@

			$$
			\sigma := \texttt{salt} \parallel
			h_1 \parallel
			punctured\_keys \parallel
			[\delta_A^{[e]}]_{e\in[1,\tau]} \parallel
			[\delta_B^{[e]}]_{e\in[1,\tau]} \parallel
			$$
			$$
			[\vec{\delta}_x^{[e]}]_{e\in[1,\tau]} \parallel [\vec{\delta}_y^{[e]}]_{e\in[1,\tau]} \parallel
			[(X_1 + t_0(\vec{u} \cdot \vec{x}))^{[e]}]_{e\in[1,\tau]} \parallel
			[(X_2 + t_0(\vec{v} \cdot \vec{x}))^{[e]}]_{e\in[1,\tau]} \parallel
			$$
			$$
			[(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{[e]}]_{e\in[1,\tau]} \parallel
			[(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{[e]}]_{e\in[1,\tau]}
			$$
		\end{tcolorbox}
